---
title: "Assignment 2 - Rama Kanetkar, Zhengping Duan, Ziqi Liu"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r preparation}
library(tidyverse)
library(reshape2)
library(ggplot2)
library(xts)
library(zoo)
house.data <- read.csv("kc_house_data.csv")
```

SECTION 1: Location analysis
This section analyses the relationship between location and house price. The involved columns are: 1) Zip code 2) latitude 3) longititude

```{r}
price_location <- house.data[,c(3,17,18,19)]
zipCode_Price <- price_location[,c(1,2)]
groupped <- melt(zipCode_Price,id.vars = c("price","zipcode")) %>% group_by(zipcode)
priceByZipcode <- groupped %>% summarise( price = mean(price))
priceByZipcode <- priceByZipcode[order(-priceByZipcode$price),]
priceByZipcode$zipcode <- factor(priceByZipcode$zipcode, levels = priceByZipcode$zipcode)
TopTenPrice <- head(priceByZipcode,n = 10) 
```

```{r Draw Plot}
ggplot(TopTenPrice, aes(x=TopTenPrice$zipcode, y=TopTenPrice$price)) + 
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Ordered Mean Price&Zip Chart", 
       subtitle="Price Vs Zipcode", 
       caption="source: US dollar") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))
```

SECTION 2: Time series analysis
Involved column: Date

```{r}
library(zoo)

housePriceByTime <- house.data[,c(2,3)]
housePriceByTime[,1]<- substr(housePriceByTime[,1],start = 1,stop = 8)
housePriceByTime[,1]<- as.Date(housePriceByTime[,1],"%Y%m%d")
housePriceByTime$price <- as.numeric(housePriceByTime$price)
housePriceByTime <- xts(as.matrix(housePriceByTime[,-1]), order.by = housePriceByTime$date)

```

```{r}
xts5_quarterly <- split(housePriceByTime,f="quarters")
quaterlyAvgPrice <- lapply(xts5_quarterly,FUN=mean)
df <- data.frame("price" = round(as.numeric(quaterlyAvgPrice),2),"quarter"=c("2014Q2","2014Q3","2014Q4","2015Q1","2015Q2"))


ggplot(data=df,mapping = aes(x = df$quarter,y = df$price))+
  geom_bar(stat="identity", width=.5, fill="tomato3") + 
  labs(title="Ordered Mean Price&Quarter", 
       subtitle="Price Vs quarter", 
       caption="source: US dollar") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))

```

SECTION 3: House condition analysis
Invovled column: 1) condition 2_ year_built 3) year_renovated
This section aims to analyze the correlation between the condition of the house and the selling price. 

```{r}
HouseCondition <- house.data[,c(3,11,15,16)]

cor.test(HouseCondition$price,HouseCondition$condition)

cor.test(HouseCondition$price,HouseCondition$yr_built)

ggplot(HouseCondition, aes(x=yr_built, y=price)) + 
  geom_point() + 
  geom_smooth(method="loess", se=F) + 
  labs(subtitle="Price Vs built year", 
       y="Price", 
       x="year Built", 
       title="Scatterplot" )

cor.test(HouseCondition$price,HouseCondition$yr_renovated)
revocated_Yes <- HouseCondition[HouseCondition[,4]!= 0,]
ggplot(revocated_Yes, aes(x=yr_renovated, y=price)) + 
  geom_point() + 
  geom_smooth(method="loess", se=F) + 
  labs(subtitle="Price Vs built year", 
       y="Price", 
       x="year renovated", 
       title="Scatterplot" )

```

SECTION 4: Grade analysis
Invovled coloumn: grade
Each buyers have grade of each house given by real estate agency for reference. We want to exam if the associated grade will influence the price of the house

```{r}
HouseGrade <- house.data[,c(3,12)]
fit <- lm(HouseGrade$price~HouseGrade$grade)

ggplot() +
  geom_point(aes(x = HouseGrade$grade, y =HouseGrade$price),
             colour = 'red') +
  geom_line(aes(x = HouseGrade$grade, y = fit$coefficients[1]+fit$coefficients[2]*as.numeric(HouseGrade$grade)),
            colour = 'blue') +
  ggtitle('Grade vs Price') +
  xlab('Grade') +
  ylab('Price')

```

SECTION 5: View Analysis
Invovled column: view
In this section, we want to analyze if house price is related to number of views by other potential buyers. We suspect that more views might result high price.

```{r}
colnames(house.data)
HouseView <- house.data[,c(3,10)]
cor.test(HouseView$price,HouseView$view)
```


SECTION 6: House features analysis
The inolved columns in this section are: 1) bedrooms 2) bathrooms 3) sqft_living 4) sqft_ot 5) floors 6) waterfront 7) sqft_above 8) sqft_basement 9) sqft_living15 10) sqft_lot15
The section below analyzes the correlation between price and each attribute. It aims to find the highly correlated features that can be applied in the house price prediction model.

```{r hourse features}
house.infrastruct = house.data[,c(1,3,4,5,8,9,13,14,20,21)]
head(house.infrastruct)

```


```{r house features summary}
sapply(house.infrastruct,summary)
```
```{r defin aggregate function}
find.aggregate <- function(agg.col,grpby.col) {

  tempDF <- aggregate(agg.col ~ grpby.col, house.infrastruct,mean)
  barplot(tempDF$agg.col,ylab = "House Price", names.arg = tempDF$grpby.col)
}
```


```{r}
cor.test(house.infrastruct$price,house.infrastruct$bedrooms)
find.aggregate(house.infrastruct$price,house.infrastruct$bedrooms)
```

```{r}
cor.test(house.infrastruct$price,house.infrastruct$bathrooms)
find.aggregate(house.infrastruct$price,house.infrastruct$bathrooms)
```

```{r}
cor.test(house.infrastruct$price,house.infrastruct$floors)
find.aggregate(house.infrastruct$price,house.infrastruct$floors)
```

```{r}
cor.test(house.infrastruct$price,house.infrastruct$waterfront)
find.aggregate(house.infrastruct$price,house.infrastruct$waterfront)
```

```{r}
cor.test(house.infrastruct$price,house.infrastruct$sqft_above)

cor.test(house.infrastruct$price,house.infrastruct$sqft_basement)

cor.test(house.infrastruct$price,house.infrastruct$sqft_living15)

cor.test(house.infrastruct$price,house.infrastruct$sqft_lot15)

```

```{r}
cor(house.infrastruct)
```


